The problem and promise of scale in multilayer networks

### 2019-12-08 paper/introduction.Rmd
start second

<!-- Social proximity scale 
sociality exists 
-->
Social scale is the type of social relationship measured and how this relationship is defined [@farine2015]. If the greater range of a social relationship is the entire social system for an organism, a particular social scale may focus on only a limited type of relationship like grooming or aggression.

>>>>

<!-- Social proximity scale 
sociality exists 
-->
Sociality is important because conspecifics have positive and negative benefits

Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007]. Positive effects include protection from predators, mating opportunities, and resource location and access [@silk2007]. Negative effects include increased competition, risk of disease transfer and infection [@silk2007].

Social scale is the type of social relationship measured and how this relationship is defined [@farine2015]. If the greater range of a social relationship is the entire social system for an organism, a particular social scale may focus on only a limited type of relationship like grooming or aggression.
